Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-28 paper.qmd
Update paper.qmd

The `rxp_populate()` function translates this [R]{.proglang} list into a
`pipeline.nix` file, which declaratively defines the entire workflow. Data flows
from derivation to derivation by being serialised into the efficient and
language-agnostic Arrow format using the pair of `encoder/decoder` functions.
Other universal formats, such as `csv` or `json` could have been used.

>>>>

The `rxp_populate()` function translates this [R]{.proglang} list into a
`pipeline.nix` file, which declaratively defines the entire workflow. Data flows
from derivation to derivation by being serialised into the efficient and
language-agnostic Arrow format using the pair of `encoder/decoder` functions.
Other universal formats, such as `csv` or `json` could have been used. It should
also be noted that if interoperability libraries such as [reticulate]{.pkg} or 
[rds2py]{.pkg} are available, it becomes possible to seamlessly transfer
supported objects to and from [R]{.proglang} and [Python]{.proglang} (for now,
such a feature is not yet integrated for conversion of arbitrary [Julia]{.proglang} objects).
